Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-26 paper/ijcai16.tex
paper: simplify slightly.

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility
becomes:
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
The generalized problem is obtained by substituting $\vw^i$ with $\vv^i := \vw_B^i + C^\top \vv_B^i$ and $p^{i,j}_z$
with $q^{i,j}_z := (\vw^i_B + C^\top \vw^i_R)_z x^j_z$ in the MILP problem.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$
%
As can be seen, non-negativity of $C$ is required for the weights $\{\vv^i\}$
to be non-negative. \andrea{check formulation}

>>>>

First, we rewrite the weight vector as $\vw = (\vw_B;\vw_R)$. The utility
becomes:
%
$$ \langle \vw, \vx \rangle = \langle \vw_B, \vx_B \rangle + \langle \vw_R, C \vx_B \rangle = \langle \vw_B + C^\top \vw_B, \vx_B \rangle $$
%
The generalized problem is obtained by substituting $\vw^i$ with $\vv^i := \vw_B^i + C^\top \vv_B^i$ and $p^{i,j}_z$
with $q^{i,j}_z := \vv^i_z x^j_z$ in the MILP problem.
All constraints remain the same, except Eq.~\ref{eq:wbounds2}, which must be
rewritten in terms of $\vv^i$:
%
$$ \forall \; i \in [k] \;.\; (\vw_B^\bot + C^\bot \vw_R) \le \vv^i \le (\vw_B^\top + C^\top \vw_R^\top)$$
%
As can be seen, non-negativity of $C$ is required for the weights $\{\vv^i\}$
to be non-negative. \andrea{check formulation}
